---
title: "Homework 5"
author: "Yihan Xu"
date: "October 8, 2015"
output: html_document
---

# download and read in the first data set
```{r}
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv "
setwd("/users/call_me_bgdrgn/documents/data science 6306")
download.file(fileURL,destfile = "gdp.csv",method="curl")
gdp <- read.csv(file="gdp.csv",header = T)
names(gdp)
head(gdp)
gdp <- read.csv(file="gdp.csv",skip=5,header = F)
head(gdp)
gdp <- read.csv(file="gdp.csv",skip=5,header = F,na.strings = c("..","Not Available."))
str(gdp)
gdp <- read.csv(file="gdp.csv",skip=5,header = F,na.strings = c("..","Not available.","..Not available"),stringsAsFactors = F)
str(gdp)
gdp <- dplyr::select(gdp,V1,V2,V4,V5)
str(gdp)
#cleaning the data
names(gdp) <- c("CountryCode","Ranking","Economy","GDP")
str(gdp)
gdp$Ranking <- as.numeric(gdp$Ranking)
str(gdp)
tail(gdp,40)
sum(is.na(gdp$Ranking))
dim(gdp)
326-136
gdp[185:195,]
summary(gdp[191:326,])
gdp <- gdp[1:191,]
str(gdp)
gdp2 <- gdp
gdp2$GDP <- as.numeric(gdp$GDP)
str(gdp2)
gdp$GDP <- gsub(",","",gdp$GDP)
str(gdp)
gdp$GDP <- as.numeric(gdp$GDP)
str(gdp)
```

# download and read in the second data set
```{r}
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
setwd("/users/call_me_bgdrgn/documents/data science 6306")
download.file(fileURL,destfile = "country.csv",method="curl")
country <- read.csv(file="country.csv",header = T)
names(country)
str(country)
new <- merge(gdp,country,by.x = "CountryCode",by.y = "CountryCode")
```
# Question1: 191-2=189 countrycode are matched from the two data sets.
```{r}
gdp3 <- gdp
gdp4 <- gdp3[order(gdp3$GDP,decreasing = F),]
gdp4[13,]
```
# Question2: the 13th country is KNA, which is St. Kitts and Nevis.
```{r}
mean(subset(new, Income.Group %in% "High income: OECD", select = c(Ranking))$Ranking)
mean(subset(new, Income.Group %in% "High income: nonOECD", select = c(Ranking))$Ranking)
```
# Question3: the average GDP rankings for the "High income: OECD" is 32.96667, and the average GDP rankings for the "High income: nonOECD" is 91.91304.
```{r}
library(Hmisc)
new$Rank.Groups=cut2(new$Ranking,g=5)
table(new$Income.Group,new$Rank.Groups)
```
# Question4: 16 countries are lower middle income but among the 38 nations with highest GDP.
```



