---
title: "Homework6"
author: "Yihan Xu"
date: "November 16, 2015"
output: html_document
---

```{r explore the dependence of the probability}
library(Sleuth3)
data(ex1223)
summary(ex1223)
str(ex1223)
help(ex1223)
ex1223$esteem[ex1223$Esteem1==1] <- 1
ex1223$esteem[ex1223$Esteem1==2] <- 0
ex1223$esteem[ex1223$Esteem1==3] <- 0
ex1223$esteem[ex1223$Esteem1==4] <- 0
ex1223$logannualincome <- log(ex1223$Income2005)
ex1223.glm <- glm(ex1223$esteem~ex1223$logannualincome+ex1223$AFQT+ex1223$Educ+ex1223$Gender,family="binomial")
summary(ex1223.glm)
confint(ex1223.glm)
exp(coef(ex1223.glm))
exp(cbind(OR = coef(ex1223.glm), confint(ex1223.glm)))
```

# equation: esteem = -2.77 + 0.17logannualincome + 0.008afqt + 0.076educ - 0.15gendermale
# When logaunnualincome increases by 1 unit, esteem will be increased by 0.17 units. When allengence increases by 1 unit, esteem will be increased by 0.008 units, when years of education increases by 1 unit, esteem will be increased by 0.076 units, gender of male will decrease esteem by 0.15. 
```{r tree}
library(rpart)
tree <- rpart(esteem~Educ+AFQT+logannualincome+Gender, data=ex1223, method="class")
print(tree)
```

```{r}
# obtain training and test sets
library(ada)
splitdf <- function(dataframe, seed=NULL) {
 if (!is.null(seed)) set.seed(seed)
 index <- 1:nrow(dataframe)
 trainindex <- sample(index, trunc(length(index)/2))
 trainset <- dataframe[trainindex, ]
 testset <- dataframe[-trainindex, ]
 list(trainset=trainset,testset=testset)
} 
keep <- c("esteem","Educ","logannualincome","Gender","AFQT")
newdata <- ex1223[keep]
splits <- splitdf(newdata,seed=808)
str(splits)
training <- splits$trainset
testiing <- splits$testset
ex.ada <- ada(esteem~.,data=training,iter=20,type="discrete")
names(ex.ada)
plot(ex.ada,test=TRUE)
extest.ada <- ada(esteem~.,data=testiing,iter=20,type="discrete")
names(extest.ada)
plot(extest.ada,test=TRUE)
test.fit <- glm(esteem~Educ+AFQT+logannualincome+Gender,data=testiing,family="binomial")
prob.fit <- predict(test.fit,testiing,type="response")
pred.fit <- rep("0",784)
pred.fit[prob.fit>0.5] <- "1"
# create confusion table
table(predicted=pred.fit,actual=testiing$esteem)
table(predicted=pred.fit,actual=testiing$Educ)
table(predicted=pred.fit,actual=testiing$Gender)
table(predicted=pred.fit,actual=testiing$logannualincome)
table(predicted=pred.fit,actual=testiing$AFQT)
```

# Not all veriables needed to obtain the best classification, because only the variabls of esteem and Gender are discrete, Educ, logannualincome and AFQT are all continuous variables. It will only make sense if make confusion table by using discrete variables.
# esteem is the best classifier.



